---
title: "Shinyapp_ReadingList"
author: "Susan Yuan"
date: "1/14/2021"
output: slidy_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Texas Bluebonnet Award 1981-2020

This Shiny Application is to provide users the information about Texas Bluebonnet Book Award winners from 1981 to 2020



### What is Texas Bluebonnet Award?

- Thousands of children voted every year
- Students in grades three through six voted
- Children had to read at least five of the books on the Texas Bluebonnet Award List and vote

## How to use this Shiny app?


- Select the year of interest from 1981 to 2020

- The title of the winner book will be presented.

## ui.R code

```{r echo = TRUE}
library(shiny)
shinyUI(fluidPage(

    # Application title
    titlePanel("The book Won Texas Bluebonnet Award 1981-2020"),

    # Input year
   
       numericInput(inputId="year","Year:1981-2020", value=2020, 
                 min=1981, max=2020, step=1),

        # Show the winnder of the year
        mainPanel(
            h3("The Title of the Book:"),
            textOutput(outputId="title")
        )
        

    
))

```

## server.R code

```{r, echo=TRUE}
library(shiny)
library(dplyr)

# Define server logic required to draw a histogram
shinyServer(function(input, output) {
    
    output$title <- renderText({
        
        master_list<-read.csv("reading_list.csv")

        winner<-master_list%>%filter(Year==input$year)
        as.character(winner$Title)

    })

})
```

